\documentclass[10pt, a4paper]{article}

% --- Base Packages ---
\usepackage[a4paper, left=1.5cm, right=1.5cm, top=1.5cm, bottom=1.5cm]{geometry}
\usepackage{fontspec}
\usepackage[english, bidi=basic, provide=*]{babel}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

% --- Font Configuration ---
\babelprovide[import, onchar=ids fonts]{english}
\babelfont{rm}{Noto Sans}

% --- Style Configuration ---
\pagestyle{empty}
\raggedright
\definecolor{darkblue}{RGB}{0, 51, 102}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt}

\titleformat{\section}{\large\bfseries\color{darkblue}\uppercase}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{8pt}

% --- Document Start ---
\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge \bfseries SONI DIEDHIOU} \\
    \vspace{4pt}
    {\large \bfseries 2nd Year Student - ENSIIE School of Engineering} \\
    \vspace{6pt}
    \small
    \href{mailto:sondiedh@gmail.com}{sondiedh@gmail.com} $|$ +33 6 88 87 66 21 $|$ Paris Area, France \\
    \vspace{2pt}
    \href{https://www.linkedin.com/in/soni-diedhiou-30b291348}{LinkedIn: soni-diedhiou} $|$ 
    \href{https://github.com/sondiedh-sys}{GitHub: sondiedh-sys} $|$ 
    \href{https://soni-diedhiou-portfolio.vercel.app}{Portfolio: soni-diedhiou-portfolio.vercel.app} \\
    \vspace{4pt}
    \textit{Seeking a Cybersecurity Internship (May to Sept) | Passionate about computer systems and network security.}
\end{center}

% --- EDUCATION ---
\section{Education}
\textbf{ENSIIE - National School of Computer Science for Industry and Business} \hfill \textbf{2024 -- 2027} \\
Master of Science in Engineering - Computer Science \& Applied Mathematics \hfill \textit{Evry, France} \\
Projected Double Degree (3rd year): \textbf{Master SECRETS} - Cybersecurity, Systems and Network Security. \\
Software Engineering track. Focus on software development and systems architecture. \\

\vspace{4pt}
\textbf{Asia Pacific University (APU)} \hfill \textbf{2025} \\
Academic Exchange Semester - Master of Science in Cybersecurity \hfill \textit{Kuala Lumpur, Malaysia} \\
Courses: Information Security Architecture (ISA), Design (ISD), SOC, Cyber Threats (CST), Network Design Performance (NDP). \\

\vspace{4pt}
\textbf{Lycée Michelet} \hfill \textbf{2022 -- 2024} \\
Preparatory Classes for Grandes Écoles (CPGE) - Math, Physics, CS \hfill \textit{Vanves, France} \\
Intensive two-year program preparing for competitive entrance exams to top engineering schools. \\

\vspace{4pt}
\textbf{Lycée des Sept Mares} \hfill \textbf{2022} \\
French General Baccalaureate - \textbf{Highest Honors (Mention Très Bien)} \hfill \textit{Maurepas, France}

% --- PROFESSIONAL EXPERIENCE ---
\section{Professional Experience}

\textbf{CNAM (National Conservatory of Arts and Crafts)} \hfill \textbf{June -- July 2025} \\
\textit{Web Development and Statistics Intern} \\
Project Link: \href{https://sondiedh.pythonanywhere.com}{sondiedh.pythonanywhere.com}
\begin{itemize}
    \item Designed statistical data visualization tools.
    \item Tech stack: Python (Flask), HTML/CSS.
\end{itemize}

\vspace{6pt}

\textbf{Auchan} \hfill \textbf{Since 2024} \\
\textit{Multi-skilled Employee (Part-time Permanent Contract) - Produce Section}
\begin{itemize}
    \item Managed inventory, organized shelves, and handled deliveries.
    \item Developed professional rigor and organizational skills in a fast-paced environment.
\end{itemize}

% --- TECHNICAL PROJECTS ---
\section{Technical Projects (ENSIIE)}

\textbf{Multi-site Office Management System} \hfill \textit{Java \& UML}
\begin{itemize}
    \item Modeled and implemented a complex workspace management system.
\end{itemize}

\vspace{6pt}

\textbf{Game Development \& Logic} \hfill \textit{C \& Python}
\begin{itemize}
    \item Programmed game mechanics integrating probabilistic logic.
\end{itemize}

\vspace{6pt}

\textbf{Image Processing \& System Interface} \hfill \textit{C, C++ \& Qt}
\begin{itemize}
    \item Developed image processing algorithms and a file management system interface.
\end{itemize}

% --- SKILLS & INTERESTS ---
\section{Skills \& Interests}
\begin{itemize}
    \item \textbf{Languages:} Python, C, Java, C++, JavaScript, SQL, PHP, Shell/Linux.
    \item \textbf{Security \& Networking:} Cisco Packet Tracer, NetSim, MSSGUARD (SOC), Windows Event Viewer.
    \item \textbf{Cyber Training:} Regular practice on TryHackMe, Root-me, OverTheWire, Network Academy.
    \item \textbf{Languages:} French (Native), English (B2 Certified), German (Beginner), Spanish (Beginner), Arabic (Beginner - Self-taught).
    \item \textbf{Interests:} Competitive Football (School team), Gym training, Video games (Action/Adventure, Arcade).
\end{itemize}

\end{document}